### 2013-04-30 inst/examples/BUGS/parametric.Rmd
breaking out sections from allen.Rmd for individual testing.

# posterior distributions
ggplot(par_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity", alpha=0.7) +
  geom_line(data=par_prior_curves, aes(x=value, y=density), col="red") + 
  facet_wrap(~ variable, scale="free", ncol=2)

>>>>

# posterior distributions
ggplot(par_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity", alpha=0.7) +
  #geom_line(data=par_prior_curves, aes(x=value, y=density), col="red") + 
  facet_wrap(~ variable, scale="free", ncol=2)

### 2013-04-30 inst/examples/BUGS/setup.Rmd
breaking out sections from allen.Rmd for individual testing.

```{r obs, dependson="sdp-pars"}
  #harvest <- sort(rep(seq(0, .5, length=7), 5))
  x <- numeric(Tobs)
  x[1] <- 6
  nz <- 1
  for(t in 1:(Tobs-1))
    x[t+1] = z_g() * f(x[t], h=0, p=p)
  obs <- data.frame(x = c(rep(0,nz), 
                          pmax(rep(0,Tobs-1), x[1:(Tobs-1)])), 
                    y = c(rep(0,nz), 
                          x[2:Tobs]))
```

>>>>

```{r obs, dependson="sdp-pars"}
  #harvest <- sort(rep(seq(0, .5, length=7), 5))
  x <- numeric(Tobs)
  x[1] <- 6
  nz <- 1
  for(t in 1:(Tobs-1))
    x[t+1] = z_g() * f(x[t], h=0, p=p)
  obs <- data.frame(x = c(rep(0,nz), 
                          pmax(rep(0,Tobs-1), x[1:(Tobs-1)])), 
                    y = c(rep(0,nz), 
                          x[2:Tobs]))
write.csv(obs, "obs.txt")
```
